Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-29 DQC3-article.tex
Simplify comments on "The Concept of Contextuality and its..."
Because I think I understand a little bit more about contextuality
maybe...

\documentclass[english,12pt]{iopart}
\usepackage{mathrsfs}
\usepackage{fullpage}
\usepackage{url}
\usepackage{times}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{iopams}
\usepackage{setstack}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% these went missing?
% \newcommand{\bra}[1]{\left\langle{#1}\right|}
% \newcommand{\ket}[1]{\left|{#1}\right\rangle}
% \newcommand{\mathscr}[1]{{\cal #1}}
%\renewcommand{\author}[1]{\bf #1 \/}
\newcommand{\affiliation}[1]{\parbox{5.5in}{\small{\it #1 \/}}}

@@

\newcommand{\fnorm}[1]{\mathsf{N}(#1)}
\newcommand{\mod}{\mbox{mod }}

@@

\title{Contextuality and Nonlocality in Discrete Quantum Theory}

\author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
Amr Sabry$^{2}$, Yu-Tsung Tai$^{4,2}$}

\address{$^{1}$ Department of Physics and Astronomy, University of California,
Los Angeles, CA 90095, USA}

\address{$^{2}$ School of Informatics and Computing, Indiana University,
Bloomington, IN 47405, USA}

\address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
47405, USA}

\address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
IN 47405, USA}

\ead{ortizg@indiana.edu}
\begin{abstract}
\today
\end{abstract}

@@

\noindent{\it Keywords\/}: {contextuality, nonlocality, measurement process, Gleason's theorem,
Bell's theorem, the Kochen-Specker theorem}

\submitto{\jpa}

@@

\yutsung{Does the sentences in this paragraph contradict to each
other? According to the postulates in page 206 and 207 in Peres~\cite{peres1995quantum},
this paragraph should read ``Quantum Physics is contextual, meaning
that if we predetermine definite outcomes for any measurement, then
the predetermined outcomes depend not only on the choice of the measured
observable(s) and on the system being measured, but also on the details
of the measurement process. To be more precise, as noted by Peres~\cite{peres1995quantum}
and Mermin~\cite{MerminPRL1990}, the result of measuring an observable
in a physical system must not depend on whether we measure the observable
alone, or along with arbitrary sets of mutually commuting observables.
However, if we try to predetermine definite measurement outcomes for
all observables on a system, the predetermined outcome of an observable
$\mathbf{O}$ will be changed by measuring other observables commuting
to $\mathbf{O}$.''}

\yutsung{Personal note about the reason why the quantum physics is
contextuality, and a bit of literature review. Don't know whether
or where to put them in our paper through.

In order to prove by contradiction, assume the quantum physics is
non-contextuality, i.e., 
\begin{enumerate}
\item \label{enu:non-contextuality}Given an observable $\mathbf{O}$, we
can predetermine a definite measurement outcome $v\left(\mathbf{O}\right)$
not depending on the choice of compatible observables that may be
preformed together with it. (postulate I in page 207 in \cite{peres1995quantum}).
\end{enumerate}
This leads to the premise of the Kochen-Specker theorem
\begin{enumerate}[resume]
\item \label{enu:premise}We can also define $v$ on states by $v\left(\ket{n}\right)=v\left(\proj{n}\right)$.
If $\left\{ \ket{n}\right\} $ forms a orthonormal basis, then $\sum_{n}v\left(\ket{n}\right)=1$.
(page 196 in \cite{peres1995quantum}).
\end{enumerate}
The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
to be satisfied so that Postulate (\ref{enu:non-contextuality}) fails,
and the quantum theory is contextual .

Because lack of commuting observables in their theory, Schumacher
and Westmoreland~\cite{2010arXiv1010.5452S} uses ``$v$ is well-defined
on states'' instead of Postulate (\ref{enu:non-contextuality}) as
the definition of non-contextuality. However, comparing to Postulate
(\ref{enu:non-contextuality}), it is less clear why ``$v$ is well-defined
on states'' should be a postulate or not.

There is no solid reason why people assume Postulate (\ref{enu:non-contextuality})
as a postulate. Peres gives a ``psychological reason'' that Postulate
(\ref{enu:non-contextuality}) is true when the measurement outcome
is predictable. Another ``psychological reason'' might be: because
Postulate (\ref{enu:non-contextuality}) is true when we replace the
``predetermined definite outcome'' by the usual ``measurement result''
in CQT. However, in DQT, because commuting observables cannot be measured
simultaneously, it may not be surprising that Postulate (\ref{enu:non-contextuality})
is false.}

@@

\yutsung{I don't understand the last sentence...}

@@

Our fundamental divergence from CQT is to replace continuous complex
amplitudes in the field of complex numbers $\C$ by discrete fields
$\ff{p^{2}}$.  If we restrict ourselves to odd primes with
$p\equiv 3\mod 4$, the fields $\ff{p}$ are exactly those for which
$x^2+1$ has no root in the field, and we can adjoin $\rmi$ as a
root of $x^2+1$ to the field $\ff{p}$.  For a given element
$\alpha \in \ff{p^2}$, we define the equivalent of complex conjugation
as the map $\alpha\mapsto\alpha^p$, which we may write as
$\alpha^*=\alpha^p$. The resulting extended field is isomorphic to
$\ff{p^2}$ and is a realization of discrete complex numbers suitable
for quantum mechanical calculations.

@@

\mathbf{H}_{1}=\left(\begin{array}{ccc}
-1 & -\rmi & 0\\
\rmi & 1 & -\rmi\\
0 & \rmi & 1
\end{array}\right)

@@

 The dimension of an eigenspace may be less than the multiplicity
of its eigenvalue. For example, consider a Hermitian matrix 

@@

\mathbf{H}_{2}=\left(\begin{array}{cc}
-1 & -1-\rmi\\
-1+\rmi & 0
\end{array}\right)

@@

The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\left(\begin{array}{cc}
1 & -1+\rmi\end{array}\right)^{T}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$

@@

$1$ with the post-measurement state $\left(\begin{array}{cc}
1 & -1+\rmi\end{array}\right)^{T}$. However, only operator always producing $1$ is the identity operator

@@

\mathbf{H}_{3}=\left(\begin{array}{cc}
-1 & -1-\rmi\\
-1+\rmi & -1
\end{array}\right)

@@

are $-1-\rmi$ with $\left(\begin{array}{cc}
1 & -1-\rmi\end{array}\right)^{T}$ and $-1+\rmi$ with $\left(\begin{array}{cc}
1 & 1+\rmi\end{array}\right)^{T}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the

@@

-1\pm\sqrt{2} & \equiv & -1\pm\rmi\left(\bmod p\right)

@@

preserved when we map them into finite fields. \yutsung{Although
may not need to type it down, need to check the definition of the
map, passing congruence into square root, and partial homomorphism...
etc.}

@@

For $i=0,1,2$ let $U_i$ be the unitary map that permutes the basis
vectors $\ket{0}$ and $\ket{i}$ and acts as the identity for the rest.
Note that $\ket{\Psi}$ is invariant under $U_i$. So again by property
({\bf iii}) we have
\[
\dpt\big(\ket{\Psi},\ket{i}\big) =\dpt\big(U_i\ket{\Psi},U_i\ket{0}\big)=
\dpt\big(\ket{\Psi},\ket{0}\big) = \frac{1}{2}
\]
for $i=0,1,2$.  These probability assignments are inconsistent with
the requirement that the probabilities for orthogonal outcomes add up
to 1. By property ({\bf i})
\begin{eqnarray*}
1 & = & \dpt\big(\ket{\Psi},\ket{0}\big)+\dpt\big(\ket{\Psi},\ket{1}\big)+\dpt\big(\ket{\Psi},\ket{2}\big)+\dpt\big(\ket{\Psi},\ket{3}\big)\\
 & = & \frac{1}{2}+\frac{1}{2}+\frac{1}{2}+\dpt\big(\ket{\Psi},\ket{3}\big)\\
 & \geq & \frac{3}{2},
\end{eqnarray*}
so we have a contradiction. The assumption of a satisfactory map
$\dpt$ is thus false. $\Box$
\end{proof}
(It should be pointed out that the argument above explicitly uses
states from a vector space of four dimensions or larger, and thus does
not hold if the largest vector space one can consider has dimension
$d\le 3$.  But it does hold for any system that, for example, contains
more than a single qubit.)

@@

  Following the general structure in~\cite{peres1995quantum}, we will
  prove by contradiction that the theorem holds for primes (with
  $p \equiv 3 \mod 4$) with $p > 3$ ~\footnote{\label{fn:p>3}When
    $p=3$, the Kochen-Specker theorem still holds, but the proof is
    longer.}. Suppose $v$ exists, and consider the set of all vectors
  with entries in $\left\{ 0,\pm1,\pm1\pm\rmi\right\} $. Then the
  steps in the proof can be read off from Table
  \ref{tab:proof-of-K-S}.  In each cell in Table
  \ref{tab:proof-of-K-S}, the string $xyz$ represents a state vector,
  where $x$, $y$, and $z$ can be \{ $0$, $1$, $\bar{1}\equiv -1,$
  ${+} \equiv (1+\rmi)$, ${-} \equiv (1-\rmi)$ \}, and
\[
v\left( xyz \right)= \{\textrm{possible}\, \mbox{\it or\/}\,
\textrm{impossible} \ , \]
depending on its column.  Examining the table from top to the bottom,
we will eventually get a contradiction.  The set of vectors are
invariant under interchanges of the $x$, $y$, and $z$ axess.  Hence,
we can assume
$v\left(100\right)=v\left(010\right)=\textrm{impossible}$ and
$v\left(001\right)=\textrm{possible}$.  Furthermore, $110$ and
$1\bar{1}0$ are orthogonal to $001$, so that
$v\left(110\right)=v\left(1\bar{1}0\right)=\textrm{impossible}$.  A
similar argument may be used to construct the second, third, and
fourth rows.  After we know enough values of
$v\left(\ket{\Psi}\right)$, we can find that $10{-}$, ${+}0\bar{1}$,
and $010$ is an orthogonal basis, and we already know that
$v\left({+}0\bar{1}\right)=v\left(010\right)=\textrm{impossible}$, so
$v\left(10{-}\right)=\textrm{possible}$.  Following a similar
procedure, we can continue evaluating the entire content of Table
\ref{tab:proof-of-K-S}.  We can see that $100$, $0{+}1$, and
$0\bar{1}{-}$ form an orthogonal basis, but we already know
$v\left(100\right)=v\left(0{+}1\right)=v\left(0\bar{1}{-}\right)
=\textrm{impossible}$.
This contradicts our initial assumptions. Therefore, there is no
function $v$ satisfying the conditions.
\end{proof}
Notice that this proof applies for almost all $p$, and, despite
the exclusive appearance of integers in $\ff{p^{2}}$ throughout the
computation, there are no occurrences of wrapping back to zero in the
number field.

@@

\section*{References}

\bibliographystyle{iopart-num}
\bibliography{discreteGBKS}

@@

\begin{enumerate}
\item Possible or impossible needed, if then inconsistent requires extends. 
\item At first assume non-degenerate for clarity, but degenerate state will
play an important rule in final analysis.
\item Review of CQT notation with pointers to DQT glitches. 
\end{enumerate}
\item Elementary tests, e.g., yes/no questions, are represented by projectors
in a complex vector space <cite Peres>
\begin{equation}
\hat{P}_{\mathcal{H}_{n}}\equiv\sum_{g_{n}=0}^{d_{n}-1}\frac{\left|n^{g_{n}}\right\rangle \bra{n^{g_{n}}}}{\ip{n^{g_{n}}}{n^{g_{n}}}}\textrm{ ,}\label{eq:projection-1}
\end{equation}
where 
\begin{equation}
{\cal O}\,\left|n^{g_{n}}\right\rangle =\lambda_{n}\left|n^{g_{n}}\right\rangle \textrm{ .}
\end{equation}
 allow degenerate extension to 
\begin{equation}
{\cal O}\,\left|n\right\rangle =\lambda_{n}\left|n\right\rangle \textrm{ .}
\end{equation}
where the set labeled by $\dpr _{n}$ has same eigenvalue $\lambda_{n}$.\end{itemize}

>>>>

\documentclass[english,12pt]{article}
\usepackage{mathrsfs}
\usepackage{fullpage}
% \documentclass[english,prl,aps,showpacs,preprint,floatfix,superscriptaddress]{revtex4-1} 
%\usepackage[T1]{fontenc}
% \usepackage[latin9]{inputenc}
% \setcounter{secnumdepth}{3}
\usepackage{url}
\usepackage{times}

\usepackage{amsthm}
\usepackage{amsmath}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% these went missing?
% \newcommand{\bra}[1]{\left\langle{#1}\right|}
% \newcommand{\ket}[1]{\left|{#1}\right\rangle}
% \newcommand{\mathscr}[1]{{\cal #1}}
%\renewcommand{\author}[1]{\bf #1 \/}
\newcommand{\affiliation}[1]{\parbox{5.5in}{\small{\it #1 \/}}}
\newcommand{\pacs}[1]{\bf #1 \/}

@@

\newcommand{\ComplexI}{\text{i}}
\allowdisplaybreaks
\newcommand{\fnorm}[1]{\mathsf{N}(#1)}

@@

\title{Contextuality and Nonlocality in \\ Discrete Quantum Theory}

\author{John Gardiner\\
 \affiliation{College of Physical and Mathematical Sciences, Brigham
  Young University, Provo, UT 84602, U.S.A}\\[.2in]
%% \author
Andrew J. Hanson\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}\\[.2in]
%%\author
Gerardo Ortiz \\
\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
U.S.A}\\[.2in]
%%\author
Amr Sabry\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}\\[.2in]
%%\author
Yu-Tsung Tai\\
\affiliation{Department of Mathematics, Indiana University,
  Bloomington, IN 47405, U.S.A}\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}}

%\date{\today}

@@

@@

@@

@@

Our fundamental divergence from CQT is to replace continuous complex
amplitudes in the field of complex numbers $\C$ by discrete fields
$\ff{p^{2}}$.  If we restrict ourselves to odd primes with
$p\equiv 3\mod 4$, the fields $\ff{p}$ are exactly those for which
$x^2+1$ has no root in the field, and we can adjoin $\ComplexI$ as a
root of $x^2+1$ to the field $\ff{p}$.  For a given element
$\alpha \in \ff{p^2}$, we define the equivalent of complex conjugation
as the map $\alpha\mapsto\alpha^p$, which we may write as
$\alpha^*=\alpha^p$. The resulting extended field is isomorphic to
$\ff{p^2}$ and is a realization of discrete complex numbers suitable
for quantum mechanical calculations.

@@

\mathbf{H}_{1}=\begin{pmatrix}-1 & -\ComplexI & 0\\
\ComplexI & 1 & -\ComplexI\\
0 & \ComplexI & 1
\end{pmatrix}

@@

The dimension of an eigenspace may be less than the multiplicity of
its eigenvalue. For example, consider a Hermitian matrix 

@@

\mathbf{H}_{2}=\begin{pmatrix}-1 & -1-\ComplexI\\
-1+\ComplexI & 0
\end{pmatrix}

@@

The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\begin{pmatrix}1\\
-1+\ComplexI
\end{pmatrix}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$

@@

$1$ with the post-measurement state $\begin{pmatrix}1\\
-1+\ComplexI
\end{pmatrix}$. However, only operator always producing $1$ is the identity operator

@@

\mathbf{H}_{3}=\begin{pmatrix}-1 & -1-\ComplexI\\
-1+\ComplexI & 1-
\end{pmatrix}

@@

are $-1-\ComplexI$ with $\begin{pmatrix}1\\
-1-\ComplexI
\end{pmatrix}$ and $-1+\ComplexI$ with $\begin{pmatrix}1\\
1+\ComplexI
\end{pmatrix}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the

@@

-1\pm\sqrt{2} & \equiv & -1\pm\ComplexI\left(\bmod p\right)

@@

preserved when we map them into finite fields.

@@

For $i=0,1,2$ let $U_i$ be the unitary map that permutes the basis
vectors $\ket{0}$ and $\ket{i}$ and acts as the identity for the rest.
Note that $\ket{\Psi}$ is invariant under $U_i$. So again by property
({\bf iii}) we have
\[
\dpt\big(\ket{\Psi},\ket{i}\big) =\dpt\big(U_i\ket{\Psi},U_i\ket{0}\big)=
\dpt\big(\ket{\Psi},\ket{0}\big) = \frac{1}{2}
\]
for $i=0,1,2$.  These probability assignments are inconsistent with
the requirement that the probabilities for orthogonal outcomes add up
to 1. By property ({\bf i})
\begin{align*}
  1&=\dpt\big(\ket{\Psi},\ket{0}\big)+ \dpt\big(\ket{\Psi},\ket{1}\big) + 
     \dpt\big(\ket{\Psi},\ket{2}\big)+ \dpt \big(\ket{\Psi},\ket{3}\big)\\
  &=\frac{1}{2}+\frac{1}{2}+\frac{1}{2}+\dpt\big(\ket{\Psi},\ket{3}\big)\\
  &\geq \frac{3}{2},
\end{align*}
so we have a contradiction. The assumption of a satisfactory map
$\dpt$ is thus false. $\Box$
\end{proof}
(It should be pointed out that the argument above explicitly uses
states from a vector space of four dimensions or larger, and thus does
not hold if the largest vector space one can consider has dimension
$d\le 3$.  But it does hold for any system that, for example, contains
more than a single qubit.)

@@

  Following the general structure in~\cite{peres1995quantum}, we will
  prove by contradiction that the theorem holds for primes (with
  $p \equiv 3 \mod 4$) with $p > 3$ ~\footnote{\label{fn:p>3}When
    $p=3$, the Kochen-Specker theorem still holds, but the proof is
    longer.}. Suppose $v$ exists, and consider the set of all vectors
  with entries in $\left\{ 0,\pm1,\pm1\pm\ComplexI\right\} $. Then the
  steps in the proof can be read off from Table
  \ref{tab:proof-of-K-S}.  In each cell in Table
  \ref{tab:proof-of-K-S}, the string $xyz$ represents a state vector,
  where $x$, $y$, and $z$ can be \{ $0$, $1$, $\bar{1}\equiv -1,$
  ${+} \equiv (1+\ComplexI)$, ${-} \equiv (1-\ComplexI)$ \}, and
\[
v\left( xyz \right)= \{\textrm{possible}\, \mbox{\it or\/}\,
\textrm{impossible} \ , \]
depending on its column.  Examining the table from top to the bottom,
we will eventually get a contradiction.  The set of vectors are
invariant under interchanges of the $x$, $y$, and $z$ axess.  Hence,
we can assume
$v\left(100\right)=v\left(010\right)=\textrm{impossible}$ and
$v\left(001\right)=\textrm{possible}$.  Furthermore, $110$ and
$1\bar{1}0$ are orthogonal to $001$, so that
$v\left(110\right)=v\left(1\bar{1}0\right)=\textrm{impossible}$.  A
similar argument may be used to construct the second, third, and
fourth rows.  After we know enough values of
$v\left(\ket{\Psi}\right)$, we can find that $10{-}$, ${+}0\bar{1}$,
and $010$ is an orthogonal basis, and we already know that
$v\left({+}0\bar{1}\right)=v\left(010\right)=\textrm{impossible}$, so
$v\left(10{-}\right)=\textrm{possible}$.  Following a similar
procedure, we can continue evaluating the entire content of Table
\ref{tab:proof-of-K-S}.  We can see that $100$, $0{+}1$, and
$0\bar{1}{-}$ form an orthogonal basis, but we already know
$v\left(100\right)=v\left(0{+}1\right)=v\left(0\bar{1}{-}\right)
=\textrm{impossible}$.
This contradicts our initial assumptions. Therefore, there is no
function $v$ satisfying the conditions.
\end{proof}
Notice that this proof applies for almost all $p$, and, despite
the exclusive appearance of integers in $\ff{p^{2}}$ throughout the
computation, there are no occurrences of wrapping back to zero in the
number field.

@@

\bibliographystyle{plain}
\bibliography{discreteGBKS}

@@

\begin{enumerate}
\item Possible or impossible needed, if then inconsistent requires extends. 
\item At first assume non-degenerate for clarity, but degenerate state will
play an important rule in final analysis.
\item Review of CQT notation with pointers to DQT glitches. 
\end{enumerate}
\item Elementary tests, e.g., yes/no questions, are represented by projectors
in a complex vector space <cite Peres>
\begin{equation}
\hat{P}_{\mathcal{H}_{n}}\equiv\sum_{g_{n}=0}^{d_{n}-1}\frac{\left|n^{g_{n}}\right\rangle \bra{n^{g_{n}}}}{\ip{n^{g_{n}}}{n^{g_{n}}}}\textrm{ ,}\label{eq:projection-1}
\end{equation}
where 
\begin{equation}
{\cal O}\,\left|n^{g_{n}}\right\rangle =\lambda_{n}\left|n^{g_{n}}\right\rangle \textrm{ .}
\end{equation}
 allow degenerate extension to 
\begin{equation}
{\cal O}\,\left|n\right\rangle =\lambda_{n}\left|n\right\rangle \textrm{ .}
\end{equation}
where the set labeled by $\dpr _{n}$ has same eigenvalue $\lambda_{n}$.

### 2015-11-29 DQC3.tex
Simplify comments on "The Concept of Contextuality and its..."
Because I think I understand a little bit more about contextuality
maybe...

\yutsung{Does the sentences in this paragraph contradict to each
other? Besides, are we talking about CQT or DQT here? The paragraph
only make sense if we can simultaneously measuring commuting observables
in CQT so that we could implement an observable in many different
measurement processes. For example, in CQT, we could implement $J_{z}$
in two different measurement processes: measuring $J_{z}$ directly,
or measuring $J_{z}^{2}$ and then $J_{z}$. These two processes are
the same because $J_{z}$ and $J_{z}^{2}$ are commuting, and can
measure simultaneously. However, these two processes are not the same
in DQT because the first always success, but the second one may produce
a zero-norm state in the middle. In general, observables cannot measure
simultaneously in DQT. Because the definition of contextuality is
based on simultaneously measurement in CQT, we must redefine the contextuality
in DQT to address this issue.

What does contextuality mean in CQT? Assume:
\begin{enumerate}
\item The quantum system were actually classical, i.e., we could assign
each observable~$\mathbf{O}$ a measurement result~$v\left(\mathbf{O}\right)$
before we do any measurement.
\end{enumerate}
Because whether measuring commuting observables of $\mathbf{O}$ or
not doesn't change the measurement result of $\mathbf{O}$, it is
nature to hope this property still hold if the quantum system were
actually classical. Therefore, we assume:
\begin{enumerate}[resume]
\item \label{enu:contextuality}The preassigned measurement result~$v\left(\mathbf{O}\right)$
of an observable~$\mathbf{O}$ is not changed if we measure the system
by any other observable commuting to $\mathbf{O}$. (page 207 in~\cite{peres1995quantum})
\end{enumerate}
Then, we have the premise of the Kochen-Specker theorem
\begin{enumerate}[resume]
\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
(page 196 in~\cite{peres1995quantum}).
\end{enumerate}
The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
to be satisfied, so that Assumption (\ref{enu:contextuality}) cannot
be true.

Schumacher and Westmoreland\cite{2010arXiv1010.5452S} uses Premise
(\ref{enu:premise}) as the definition of contextuality because it
seems impossible to discuss the commuting observables in their theory.
Our paper may do better and use Assumption (\ref{enu:contextuality})
as contextuality. However, it is not that surprising if Assumption
(\ref{enu:contextuality}) is false because commuting observables
cannot be measured simultaneously in DQT anyway. }

@@

\item {\it The Kochen-Specker theorem\/} in its classical form employs
  a complicated array of measurements on a single system along with
  geometric arguments to exclude additional wide classes of hidden
  variable theories~\cite{kochenspecker1967}.  The Kochen-Specker
  theorem does not depend on statistical averages, and it is geometric
  in spirit.  (More succinct approaches can be found, e.g., in
  Peres~\cite{peres1995quantum}.)  The freedom from statistical
  averages in the Kochen-Specker methods suggests that important parts
  of the result could be independent of ordered probabilities and thus
  in fact might possess suitable analogs in finite fields.  The key is
  to understand the implications of contextuality, and here we find
  that the possibility of valid null intermediate states in discrete
  quantum theory can disrupt what would seem to be trivial
  contextuality.  To deal with this, we are compelled to explicitly
  consider, not only the initial and final resources needed to
  represent the system and the final measurement outcome, but also the
  resources needed to represent the intermediate steps in a series of
  experiments. We find that, to preserve the spirit of the
  Kochen-Specker theorem, we have to explicitly introduce and propagate
  \emph{error states} whose representation requires more than the
  available resources.

@@

All of these basic insights into the structure of traditional quantum
mechanics rely on {\it contextuality\/} and {\it nonlocality\/}: We
will argue in our conclusions that, in discrete quantum theory, we can
consistently employ both contextuality, the statement that measurement
of a quantum observable does not depend on any given second observable
provided it commutes with the first observable, and, nonlocality,
which says that spatially separated measurements in a quantum theory
can in fact be correlated, counter to classical intuitions.

>>>>

\yutsung{Does the sentences in this paragraph contradict to each
other? According to the postulates in page 207 in Peres~\cite{peres1995quantum},
the last sentence should be ``To be more precise, as noted by Peres~\cite{peres1995quantum}
and Mermin~\cite{MerminPRL1990}, it is impossible to predetermine
definite measurement outcomes for all observables on a system, such
that the predetermined outcome of any observable does not depend on
whether we measure the observable alone, or along with arbitrary sets
of mutually commuting observables.''

Let $v\left(\mathbf{O}\right)$ be the predetermined definite outcome
of an observable $\mathbf{O}$, then we can define $v'$ on states
by their projector $v'\left(\ket{n}\right)=v\left(\proj{n}\right)$.
Because lack of commuting observables in Schumacher and Westmoreland~\cite{2010arXiv1010.5452S},
they use ``$v'$ is well-defined'' as the definition of non-contextuality.

Besides, if the result of measuring an observable depends on simultaneously
measuring commuting observables, then the usual slogan ``two commuting
operators can be simultaneously measured'' is just confusing... }

@@

\item {\it The Kochen-Specker theorem\/} in its classical form employs
  a complicated array of measurements on a single system along with
  geometric arguments to exclude additional wide classes of hidden
  variable theories~\cite{kochenspecker1967}.  The Kochen-Specker
  theorem does not depend on statistical averages, and it is geometric
  in spirit.  (More succinct approaches can be found, e.g., in
  Peres~\cite{peres1995quantum}.)  The freedom from statistical
  averages in the Kochen-Specker methods suggests that important parts
  of the result could be independent of ordered probabilities and thus
  in fact might possess suitable analogs in finite fields.  The key is
  to understand the implications of contextuality, and here we find
  that the possibility of valid null intermediate states in discrete
  quantum theory can disrupt what would seem to be trivial
  contextuality. \yutsung{I don't understand this sentence...} To deal with
  this, we are compelled to explicitly consider, not only the initial and final resources needed to
  represent the system and the final measurement outcome, but also the
  resources needed to represent the intermediate steps in a series of
  experiments. We find that, to preserve the spirit of the
  Kochen-Specker theorem, we have to explicitly introduce and propagate
  \emph{error states} whose representation requires more than the
  available resources.

@@

All of these basic insights into the structure of traditional quantum
mechanics rely on {\it contextuality\/} and {\it nonlocality\/}: We
will argue in our conclusions that, in discrete quantum theory, we can
consistently employ both contextuality, the statement that measurement
of a quantum observable does not depend on any given second observable
provided it commutes with the first observable, \yutsung{Should
be ``contextuality, the statement that the predetermined measurement
outcome of a quantum observable depends on any given second observable
although it may commute with the first observable''} and, nonlocality,
which says that spatially separated measurements in a quantum theory
can in fact be correlated, counter to classical intuitions.
